### 2014-06-21 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Rename files
Equipment Guide: Minor edit to path
Equipment: Add gas analyzer pictures

\input{../../Bibliography/commoncommands}

@@

\headerB{
Fire Fighting Technology \\
Equipment Guide
}

@@

\flushright{
\includegraphics[width=2.in]{../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

The internal pump is located in the center of the chassis. The O$_2$ sensor is located under the foam cover. The CO sensor is located towards the front panel of the gas analyzer, and the CO$_2$ sensor is located towards the rear panel.

>>>>

\input{../Bibliography/commoncommands}

@@

\headerB{
Fire Fighting Technology \\
Equipment and Testing Guide
}

@@

\flushright{
\includegraphics[width=2.in]{../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

An overview of the internal components of the gas analyzer is shown in Fig.~\ref{fig:gas_analyzer_5}. The internal pump is located in the center of the chassis, as shown in Fig.~\ref{fig:gas_analyzer_3}. The O$_2$ sensor is located under the foam cover. The CO sensor is located towards the front panel of the gas analyzer, and the CO$_2$ sensor is located towards the rear panel.

\begin{figure}[h!]
\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_5}
\caption{Internal components of the gas analyzer.}
\label{fig:gas_analyzer_5}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_3}
\caption{Internal pump within the gas analyzer.}
\label{fig:gas_analyzer_3}
\end{figure}
